---
title: "Mesocosm Results"
author: "Brianna Henry"
date: "September 27, 2017"
output: word_document
---
```{r}
library(brms)
library(ggplot2)
```

In all data, treatment 1 is control, treatment 2 is atrazine, treatment 3 is selenium, and treatment 4 is the atrazine and selenium combined treatment.

Adult Biomass

Adult biomass data is from the biodivnew file and is initially in g/0.36m2/4 days.

```{r}
urlfile<-"https://raw.githubusercontent.com/briannahenry/Mesocosm2/master/biodivnew.csv"
biodivnew<-read.csv(urlfile)
biodivnew$trt0f<-as.factor(biodivnew$trt0f)
biodivnew$date0f<-as.factor(biodivnew$date0f)
```

Total Biomass

Model

```{r}
get_prior(totbio~date0f+trt0f+date0f*trt0f +(1|tank),data=biodivnew,family=Gamma(link="log")) 

mbiobrm<-brm(totbio~date0f+trt0f+date0f*trt0f +(1|tank),data=biodivnew,family=Gamma(link="log"),
           prior=c(prior(cauchy(0,1),class=sd),
                   prior(normal(0,2),class=b)))
```

Model Checks

```{r}
print(mbiobrm)
pp_check(mbiobrm,type="hist")
pp_check(mbiobrm,type="boxplot")
```


Chironomid Biomass

Model

```{r}
get_prior(biochiro~trt0f+date0f+date0f*trt0f +(1|tank),data=biodivnew,family=Gamma(link="log"))

chirobio<-brm(biochiro~date0f*trt0f +(1|tank),data=biodivnew,family=Gamma(link="log"),
            prior=c(prior(cauchy(0,1),class=sd),
                    prior(normal(0,2),class=b)))
```

Model Checks

```{r}
print(chirobio)
pp_check(chirobio,type="hist")
pp_check(chirobio,type="boxplot")
```


Libellulid Biomass

Model

```{r}
get_prior(bio_odo~trt0f+date0f+date0f*trt0f +(1|tank),data=biodivnew,family=Gamma(link="log"))

odobio<-brm(bio_odo~trt0f+date0f+date0f*trt0f +(1|tank),data=biodivnew,family=Gamma(link="log"),
            prior=c(prior(cauchy(0,1),class=sd),
                    prior(normal(0,2),class=b)))
```

Model Checks

```{r}
print(odobio)
pp_check(odobio,type="hist")
pp_check(odobio,type="boxplot")
```

Example of Comparison among Treatments

Extract posterior samples and add appropriate offsets from the intercept to get estimates of abundance for each treatment on each date 

```{r}
mbiopost<-posterior_samples(mbiobrm)
str(mbiopost)

btrt1_3<-mbiopost$b_Intercept+mbiopost$b_date0f7D4D2016 #posterior treatment 1 on date 3
btrt2_3<-mbiopost$b_Intercept+mbiopost$b_date0f7D4D2016+mbiopost$b_trt0f2+mbiopost$`b_date0f7D4D2016:trt0f2`

#Trt 1 & 2 on date 3#
btrt1_2_d3<-(((exp(btrt1_3)*2.78)/4))-(((exp(btrt2_3)*2.78)/4))
mean(btrt1_2_d3)
quantile(btrt1_2_d3,probs=c(0.025,0.975)) 
sum(btrt1_2_d3>0)/4000 #87.8%
```


Preparing to Plot

Create data frame for total, chironomid, and libellulid biomass, edit date as a properly ordered factor so that it plots dates in the right order, convert estimates and upper and lower quantiles to g/m2/d.

```{r}
#TOTAL
totbplot<-marginal_effects(mbiobrm, robust=FALSE)
totbplot<-as.data.frame(totbplot$`date0f:trt0f`)
totbplot$date3<-factor(totbplot$date0f, levels = c("6/20/2016","6/28/2016", "7/4/2016", "7/12/2016", "7/18/2016", "7/26/2016", "8/2/2016"))
totbplot$est2<-(totbplot$estimate__)*2.78/4
totbplot$upper2<-(totbplot$upper__)*2.78/4
totbplot$lower2<-(totbplot$lower__)*2.78/4

#CHIRONOMID
chirbplot<-marginal_effects(chirobio, robust=FALSE)
chirbplot<-as.data.frame(chirbplot$`date0f:trt0f`)
chirbplot$date2<-factor(chirbplot$date0f, levels = c("6/20/2016","6/28/2016", "7/4/2016", "7/12/2016", "7/18/2016", "7/26/2016", "8/2/2016"))
chirbplot$est2<-(chirbplot$estimate__)*2.78/4
chirbplot$upper2<-(chirbplot$upper__)*2.78/4
chirbplot$lower2<-(chirbplot$lower__)*2.78/4

#LIBELLULID
odobplot<-marginal_effects(odobio, effects="date0f:trt0f", robust=FALSE)
odobplot<-as.data.frame(odobplot$`date0f:trt0f`)
odobplot$date2<-factor(odobplot$date0f, levels = c("6/20/2016","6/28/2016", "7/4/2016", "7/12/2016", "7/18/2016", "7/26/2016", "8/2/2016"))
odobplot$est2<-(odobplot$estimate__)*2.78/4
odobplot$upper2<-(odobplot$upper__)*2.78/4
odobplot$lower2<-(odobplot$lower__)*2.78/4
```

Combine all three data frames to one and convert data to mgDM, allowing for creation of a facetted plot, change date to day of experiment

```{r}
chirbplot$group<-"Chironomidae Adults"
odobplot$group<-"Libellulidae Adults"
totbplot$group<-"Total Adults"

totbplot$date2<-totbplot$date3
totbplot$date3<-NULL
totbplot$totbio<-NULL
chirbplot$biochiro<-NULL
odobplot$bio_odo<-NULL
adubiomass<-rbind(totbplot, chirbplot, odobplot)

adubiomass$group2<-factor(adubiomass$group, levels= c("Total Adults", "Chironomidae Adults", "Libellulidae Adults"))
adubiomass$est3<-(adubiomass$est2)*1000
adubiomass$lower3<-(adubiomass$lower2)*1000
adubiomass$upper3<-(adubiomass$upper2)*1000

adubiomass$date3<-ifelse(adubiomass$date2=="6/20/2016", "Day 0",
                     ifelse(adubiomass$date2=="6/28/2016", "Day 7",
                            ifelse(adubiomass$date2=="7/4/2016", "Day 13",
                                   ifelse(adubiomass$date2=="7/12/2016", "Day 21",
                                          ifelse(adubiomass$date2=="7/18/2016", "Day 27",
                                                 ifelse(adubiomass$date2=="7/26/2016", "Day 35", "Day 42"))))))
```

Create plot

```{r}
ggplot(adubiomass,aes(x=date3,y=est3, fill=trt0f, shape=trt0f))+
  geom_errorbar(aes(ymin=lower3, ymax=upper3), width=.1, position=position_dodge(width = 0.4))+
  geom_point(position=position_dodge(width = 0.4), size=4)+
  facet_grid(group2~., scales="free")+
  xlab("Day of Experiment")+
  ylab(expression(paste("Adult Biomass (mgDM/m"^2,"/day)")))+
  scale_shape_manual(name="Treatment", labels = c("Control", "Atrazine", "Selenium", "Atrazine and Selenium"),  values = c(21,22,23,24))+
  scale_fill_manual(name="Treatment", labels = c("Control", "Atrazine", "Selenium", "Atrazine and Selenium"),  values = c("grey0","grey35","grey70","grey100"))+
  theme_bw()+
  theme(axis.text.x = element_text(color="black"))+
  theme(axis.text.y = element_text(color="black"))+
  theme(legend.title = element_text(face="bold", size="11"),
        panel.grid = element_blank())
```

Adult Weekly Abundance

Adult abundance data also comes from the biodivnew data file, which is already imported above. Data are in # insects/0.36m2/4days.

Model

```{r}
get_prior(totno~date0f+trt0f+date0f*trt0f +(1|tank),data=biodivnew,family=poisson(link="log"))

abundadult<-brm(totno~date0f+trt0f+date0f*trt0f +(1|tank),data=biodivnew,family=poisson(link="log"),
           prior=c(prior(cauchy(0,1),class=sd),
                   prior(normal(0,5),class=b)))
```


Model Checks

```{r}
print(abundadult)
pp_check(abundadult,type="hist") 
pp_check(abundadult,type="boxplot")
```

Comparisons on a Given Date

Extract posterior samples and add appropriate offsets from the intercept to get estimates of abundance for each treatment on each date 

```{r}
m2post<-posterior_samples(abundadult)
str(m2post)

#estimate posteriors for each date*trt combination. 

trt1_2<-m2post$b_Intercept+m2post$b_date0f2 #posterior treatment 1 on date 2
trt1_3<-m2post$b_Intercept+m2post$b_date0f3 #posterior treatment 1 on date 3
trt1_4<-m2post$b_Intercept+m2post$b_date0f4 #posterior treatment 1 on date 3
trt1_5<-m2post$b_Intercept+m2post$b_date0f5 #posterior treatment 1 on date 3
trt1_6<-m2post$b_Intercept+m2post$b_date0f6 #posterior treatment 1 on date 3
trt1_7<-m2post$b_Intercept+m2post$b_date0f7 #posterior treatment 1 on date 3

trt2_2<-m2post$b_Intercept+m2post$b_date0f2+m2post$b_trt0f2+m2post$`b_date0f2:trt0f2`
trt2_3<-m2post$b_Intercept+m2post$b_date0f3+m2post$b_trt0f2+m2post$`b_date0f3:trt0f2`
trt2_4<-m2post$b_Intercept+m2post$b_date0f4+m2post$b_trt0f2+m2post$`b_date0f4:trt0f2`
trt2_5<-m2post$b_Intercept+m2post$b_date0f5+m2post$b_trt0f2+m2post$`b_date0f5:trt0f2`
trt2_6<-m2post$b_Intercept+m2post$b_date0f6+m2post$b_trt0f2+m2post$`b_date0f6:trt0f2`
trt2_7<-m2post$b_Intercept+m2post$b_date0f7+m2post$b_trt0f2+m2post$`b_date0f7:trt0f2`

trt3_2<-m2post$b_Intercept+m2post$b_date0f2+m2post$b_trt0f3+m2post$`b_date0f2:trt0f3`
trt3_3<-m2post$b_Intercept+m2post$b_date0f3+m2post$b_trt0f3+m2post$`b_date0f3:trt0f3`
trt3_4<-m2post$b_Intercept+m2post$b_date0f4+m2post$b_trt0f3+m2post$`b_date0f4:trt0f3`
trt3_5<-m2post$b_Intercept+m2post$b_date0f5+m2post$b_trt0f3+m2post$`b_date0f5:trt0f3`
trt3_6<-m2post$b_Intercept+m2post$b_date0f6+m2post$b_trt0f3+m2post$`b_date0f6:trt0f3`
trt3_7<-m2post$b_Intercept+m2post$b_date0f7+m2post$b_trt0f3+m2post$`b_date0f7:trt0f3`

trt4_2<-m2post$b_Intercept+m2post$b_date0f2+m2post$b_trt0f4+m2post$`b_date0f2:trt0f4` 
trt4_3<-m2post$b_Intercept+m2post$b_date0f3+m2post$b_trt0f4+m2post$`b_date0f3:trt0f4`
trt4_4<-m2post$b_Intercept+m2post$b_date0f4+m2post$b_trt0f4+m2post$`b_date0f4:trt0f4` 
trt4_5<-m2post$b_Intercept+m2post$b_date0f5+m2post$b_trt0f4+m2post$`b_date0f5:trt0f4` 
trt4_6<-m2post$b_Intercept+m2post$b_date0f6+m2post$b_trt0f4+m2post$`b_date0f6:trt0f4` 
trt4_7<-m2post$b_Intercept+m2post$b_date0f7+m2post$b_trt0f4+m2post$`b_date0f7:trt0f4` 
```

Comparison example

```{r}
#Trt 1 & 4 
trt1_4_d3<-(((exp(trt1_3)*2.78)/4))-(((exp(trt4_3)*2.78)/4)) 
mean(trt1_4_d3) #Average of 39 fewer insects emerging per m2 per day relative to the control on date 3
quantile(trt1_4_d3,probs=c(0.025,0.975)) 
sum(trt1_4_d3>0)/4000 #We are 95% certain that the difference in emergence between trts 1 and 4 on date 3 was greater than zero.
```


Preparing to plot

Create data frame, edit date as a properly ordered factor so that it plots dates in the right order, change date to day of experiment, convert estimates and upper and lower quantiles to #/m2/day.

```{r}
aaplot<-marginal_effects(abundadult, robust=FALSE)
aaplot<-as.data.frame(aaplot$`date0f:trt0f`)
aaplot$date2<-factor(aaplot$date0f, levels = c("6/20/2016","6/28/2016", "7/4/2016", "7/12/2016", "7/18/2016", "7/26/2016", "8/2/2016"))
aaplot$est2<-(aaplot$estimate__)*2.78/4
aaplot$upper2<-(aaplot$upper__)*2.78/4
aaplot$lower2<-(aaplot$lower__)*2.78/4

aaplot$date3<-ifelse(aaplot$date2=="6/20/2016", "Day 0",
                 ifelse(aaplot$date2=="6/28/2016", "Day 7",
                        ifelse(aaplot$date2=="7/4/2016", "Day 13",
                               ifelse(aaplot$date2=="7/12/2016", "Day 21",
                                      ifelse(aaplot$date2=="7/18/2016", "Day 27",
                                             ifelse(aaplot$date2=="7/26/2016", "Day 35", "Day 42"))))))
```

Plot

```{r}
ggplot(aaplot,aes(x=date3,y=est2, fill=trt0f))+
  geom_errorbar(aes(ymin=lower2, ymax=upper2), width=.1, position=position_dodge(width=0.4))+
  geom_point(position=position_dodge(width=0.4), size=4, shape=21)+
  xlab("Day of Experiment")+
  ylab(expression(paste("Total Adult Abundance (#/m"^2,"/day)")))+
  scale_fill_manual(name="Treatment", labels = c("Control", "Atrazine", "Selenium", "Atrazine and Selenium"),  values = c("grey0","grey20","grey50","grey80"))+
  theme_classic()+
  theme(axis.text.x = element_text(color="black"))+
  theme(axis.text.y = element_text(color="black"))+
  theme(legend.title = element_text(face="bold", size="11"))
```


Adult Cumulative Abundance 

From the above model, we use the posterior distribution to estimate the cumulative emergence from each treatment and make comparisons.

```{r}
trt1_tot<-(((exp(trt1_2)*2.78)/4))+(((exp(trt1_3)*2.78)/4))+(((exp(trt1_4)*2.78)/4))+(((exp(trt1_5)*2.78)/4))+(((exp(trt1_6)*2.78)/4))+(((exp(trt1_7)*2.78)/4))
trt2_tot<-(((exp(trt2_2)*2.78)/4))+(((exp(trt2_3)*2.78)/4))+(((exp(trt2_4)*2.78)/4))+(((exp(trt2_5)*2.78)/4))+(((exp(trt2_6)*2.78)/4))+(((exp(trt2_7)*2.78)/4))
trt3_tot<-(((exp(trt3_2)*2.78)/4))+(((exp(trt3_3)*2.78)/4))+(((exp(trt3_4)*2.78)/4))+(((exp(trt3_5)*2.78)/4))+(((exp(trt3_6)*2.78)/4))+(((exp(trt3_7)*2.78)/4))
trt4_tot<-(((exp(trt4_2)*2.78)/4))+(((exp(trt4_3)*2.78)/4))+(((exp(trt4_4)*2.78)/4))+(((exp(trt4_5)*2.78)/4))+(((exp(trt4_6)*2.78)/4))+(((exp(trt4_7)*2.78)/4))

mean(trt1_tot) #mean control 
mean(trt2_tot) #mean atrazine
mean(trt3_tot) #mean selenium
mean(trt4_tot) #mean combined

quantile(trt1_tot,probs=c(0.025,0.975)) #quantile control
quantile(trt2_tot,probs=c(0.025,0.975)) #quantile atrazine
quantile(trt3_tot,probs=c(0.025,0.975)) #quantile selenium
quantile(trt4_tot,probs=c(0.025,0.975)) #quantile combined
```

Example of comparisons among treatments

```{r}
#fold difference in cumulative emergence
diff1_4_fold<-trt1_tot/trt4_tot
quantile(diff1_4_fold, probs=c(0.025,0.975))
#0.9-2.5 fold change

#Comparing Treatments 1 & 4
diff1_4<-trt1_tot-trt4_tot #difference between treatments estimated at each of the 4000 iterations of the MCMC. 
mean(diff1_4) #Average of 90 more insects emerging from trt1 than trt4 per m2 over the 6 week period
quantile(diff1_4,probs=c(0.025,0.975)) #We are 95% certain that the true difference in cumulative emergence between trt1 and 4 was between -28 and 225
sum(diff1_4>0)/4000 #There is a 93% probability that the difference in these treatments was > 0
```


Larval Biomass

Larval biomass data is from the larvbio2 file and is in mgDM/0.032m2.

```{r}
urlfile2<-"https://raw.githubusercontent.com/briannahenry/Mesocosm2/master/larvbio2.csv"
larvbio2<-read.csv(urlfile2)
larvbio2$date0f<-as.factor(larvbio2$date)
larvbio2$trt0f<-as.factor(larvbio2$trt)
```


Total Biomass

Model

```{r}
get_prior(totbio~date0f+trt0f+date0f*trt0f +(1|tank),data=larvbio2,family=Gamma(link="log")) 

lbio<-brm(totbio~date0f+trt0f+date0f*trt0f +(1|tank),data=larvbio2,family=Gamma(link="log"),
             prior=c(prior(cauchy(0,1),class=sd),
                     prior(normal(0,2),class=b)))
```

Model Checks

```{r}
print(lbio)
pp_check(lbio,type="hist")
pp_check(lbio,type="boxplot")
```


Chironomid Biomass

Model

```{r}
get_prior(chirobio~date0f+trt0f+date0f*trt0f +(1|tank),data=larvbio2,family=Gamma(link="log")) 

chirlbio<-brm(chirobio~date0f+trt0f+date0f*trt0f +(1|tank),data=larvbio2,family=Gamma(link="log"),
          prior=c(prior(cauchy(0,1),class=sd),
                  prior(normal(0,2),class=b)))
```

Model Checks

```{r}
print(chirlbio)
pp_check(chirlbio,type="hist")
pp_check(chirlbio,type="boxplot")
```


Libellulid Biomass

Model

```{r}
get_prior(odobio~date0f+trt0f+date0f*trt0f +(1|tank),data=larvbio2,family=Gamma(link="log")) 

odolbio<-brm(odobio~date0f+trt0f+date0f*trt0f +(1|tank),data=larvbio2,family=Gamma(link="log"),
              prior=c(prior(cauchy(0,1),class=sd),
                      prior(normal(0,2),class=b)))
```

Model Checks

```{r}
print(odolbio)
pp_check(odolbio,type="hist")
pp_check(odolbio,type="boxplot")
```

Example of Comparison among Treatments

```{r}
lbpost<-posterior_samples(lbio)
str(lbpost)

#Date 7/6/16
lbtrt1_2<-lbpost$b_Intercept+lbpost$b_date0f7D6D2016
lbtrt2_2<-lbpost$b_Intercept+lbpost$b_trt0f2+lbpost$b_date0f7D6D2016+lbpost$`b_date0f7D6D2016:trt0f2`
lbtrt3_2<-lbpost$b_Intercept+lbpost$b_trt0f3+lbpost$b_date0f7D6D2016+lbpost$`b_date0f7D6D2016:trt0f3`
lbtrt4_2<-lbpost$b_Intercept+lbpost$b_trt0f4+lbpost$b_date0f7D6D2016+lbpost$`b_date0f7D6D2016:trt0f4`

#Trt 1 & 4#
lbdiff1_4<-(exp(lbtrt4_2)*31.25)-(exp(lbtrt1_2)*31.25)
mean(lbdiff1_4) 
quantile(lbdiff1_4, probs=c(0.025,0.975))
sum(lbdiff1_4>0)/4000 #87% prob that difference >0
```


Preparing to plot

Create data frame for each total larval biomass, chironomid larval biomass, and libellulid larval biomass, edit date as a properly ordered factor so that it plots dates in the right order, convert estimates and upper and lower quantiles to mgDM/m2.

```{r}
#TOTAL 
totlbplot<-marginal_effects(lbio, robust=FALSE)
totlbplot<-as.data.frame(totlbplot$`date0f:trt0f`)
totlbplot$date2<-factor(totlbplot$date0f, levels = c("6/20/2016", "7/6/2016","8/2/2016"))
totlbplot$est2<-(totlbplot$estimate__)*31.25
totlbplot$upper2<-(totlbplot$upper__)*31.25
totlbplot$lower2<-(totlbplot$lower__)*31.25

#CHIRONOMID
chirlbplot<-marginal_effects(chirlbio, robust=FALSE)
chirlbplot<-as.data.frame(chirlbplot$`date0f:trt0f`)
chirlbplot$date2<-factor(chirlbplot$date0f, levels = c("6/20/2016", "7/6/2016","8/2/2016"))
chirlbplot$est2<-(chirlbplot$estimate__)*31.25
chirlbplot$upper2<-(chirlbplot$upper__)*31.25
chirlbplot$lower2<-(chirlbplot$lower__)*31.25

#LIBELLULID
odolbplot<-marginal_effects(odolbio, robust=FALSE)
odolbplot<-as.data.frame(odolbplot$`date0f:trt0f`)
odolbplot$date2<-factor(odolbplot$date0f, levels = c("6/20/2016", "7/6/2016","8/2/2016"))
odolbplot$est2<-(odolbplot$estimate__)*31.25
odolbplot$upper2<-(odolbplot$upper__)*31.25
odolbplot$lower2<-(odolbplot$lower__)*31.25
```

Combine all three data frames to one, allowing for creation of a facetted plot, change date to day of experiment

```{r}
chirlbplot$chirobiog<-NULL
odolbplot$odobiog<-NULL
totlbplot$totbiog<-NULL
chirlbplot$chirobio<-NULL
odolbplot$odobio<-NULL
totlbplot$totbio<-NULL
chirlbplot$group<-"Chironomidae Larvae"
odolbplot$group<-"Libellulidae Larvae"
totlbplot$group<-"Total Larvae"
larv_data<-rbind(chirlbplot,odolbplot,totlbplot)
larv_data$group2<-ifelse(larv_data$group=="total_larvae", "Total Larvae",
                         ifelse(larv_data$group=="chiro_larvae", "Chironomidae Larvae", "Libellulidae Larvae"))

larv_data$group3<-factor(larv_data$group, levels=c("Total Larvae", "Chironomidae Larvae", "Libellulidae Larvae"))
larv_data$date3<-ifelse(larv_data$date2=="6/20/2016", "Day 0",
                     ifelse(larv_data$date2=="7/6/2016", "Day 15", "Day 42"))
```

Create plot

```{r}
ggplot(larv_data,aes(x=date3,y=est2, fill=trt0f, shape=trt0f))+
  geom_errorbar(aes(ymin=lower2, ymax=upper2), width=.1, position=position_dodge(width=0.4))+
  facet_grid(group3~.,scales="free")+
  geom_point(position=position_dodge(width=0.4), size=4)+
  xlab("Day of Experiment")+
  ylab(expression(paste("Larval Biomass (mgDM/m"^2,")")))+
  scale_shape_manual(name="Treatment", labels = c("Control", "Atrazine", "Selenium", "Atrazine and Selenium"),  values = c(21,22,23,24))+
  scale_fill_manual(name="Treatment", labels = c("Control", "Atrazine", "Selenium", "Atrazine and Selenium"),  values = c("grey0","grey35","grey70","grey100"))+
  theme_bw()+
  theme(axis.text.x = element_text(color="black"))+
  theme(axis.text.y = element_text(color="black"))+
  theme(legend.title = element_text(face="bold", size="11"),
        panel.grid=element_blank())
```


Larval Abundance

Larval abundace data come from the dbentab data file and are in #/0.032m2.

```{r}
urlfile3<-"https://raw.githubusercontent.com/briannahenry/Mesocosm2/master/dbentab.csv"
dbentab<-read.csv(urlfile3)
dbentab$trt0f<-as.factor(dbentab$trt)
dbentab$date0f<-as.factor(dbentab$date)
```

Model

```{r}
get_prior(nobugs~date0f+trt0f+date0f*trt0f +(1|tank),data=dbentab,family=poisson(link="log"))

larvabund<-brm(nobugs~date0f+trt0f+date0f*trt0f +(1|tank),data=dbentab,family=poisson(link="log"),
           prior=c(prior(cauchy(0,1),class=sd),
                   prior(normal(0,10),class=b)))
```

Model Checks

```{r}
print(larvabund)
pp_check(larvabund,type="hist") 
pp_check(larvabund,type="boxplot")
```

Example of Comparison among Treatments

```{r}
mlpost<-posterior_samples(larvabund)
str(mlpost)

ltrt1_1<-mlpost$b_Intercept
ltrt2_1<-mlpost$b_Intercept+mlpost$b_trt0f2

#Differences on Date 1
#Trt 1 & 2
ltrt1_2_d1<-(exp(ltrt1_1))-(exp(ltrt2_1))
mean(ltrt1_2_d1)
quantile(ltrt1_2_d1,probs=c(0.025,0.975))
sum(ltrt1_2_d1>0)/4000 #72.3% prob diff > 0
```


Preparing to plot

Create data frame, edit date as a properly ordered factor so that it plots dates in the right order, change date to day of experiment, convert estimates and upper and lower quantiles to #/m2.

```{r}
laplot<-marginal_effects(larvabund, robust=FALSE)
laplot<-as.data.frame(laplot$`date0f:trt0f`)
laplot$date2<-factor(laplot$date0f, levels = c("6/20/2016","7/6/2016","8/2/2016"))
laplot$est2<-(laplot$estimate__)*31.25
laplot$upper2<-(laplot$upper__)*31.25
laplot$lower2<-(laplot$lower__)*31.25
laplot$date3<-ifelse(laplot$date2=="6/20/2016", "Day 0",
                        ifelse(laplot$date2=="7/6/2016", "Day 15", "Day 42"))
```

Plot

```{r}
ggplot(laplot,aes(x=date3,y=est2, fill=trt0f, shape=trt0f))+
  geom_errorbar(aes(ymin=lower2, ymax=upper2), width=.1, position=position_dodge(width=0.4))+
  geom_point(position=position_dodge(width=0.4), size=4)+
  xlab("Day of Experiment")+
  ylab(expression(paste("Total Larval Abundance (#/m"^2,")")))+
  scale_shape_manual(name="Treatment", labels = c("Control", "Atrazine", "Selenium", "Atrazine and Selenium"),  values = c(21,22,23,24))+
  scale_fill_manual(name="Treatment", labels = c("Control", "Atrazine", "Selenium", "Atrazine and Selenium"),  values = c("grey0","grey35","grey70","grey100"))+
  theme_classic()+
  theme(axis.text.x = element_text(color="black"))+
  theme(axis.text.y = element_text(color="black"))+
  theme(legend.title = element_text(face="bold", size="11"))
```



Chlorophyll

Data for chlorophyll models comes from the chla data file. Units for benthic chlorphyll are in ug/cm2 and units for water column chlorophyll are in mg/l.

```{r}
urlfile4<-"https://raw.githubusercontent.com/briannahenry/Mesocosm2/master/chl.csv"
chl<-read.csv(urlfile4)
chl$trt0f<-as.factor(chl$trt)
chl$date0f<-as.factor(chl$date)
```

Benthic Chlorophyll

Model
```{r}
get_prior(bchlug_cm2_new~date0f+trt0f+date0f*trt0f +(1|tank),data=chl,family=Gamma(link="log"))

bchlbrm<-brm(bchlug_cm2_new~date0f+trt0f+date0f*trt0f +(1|tank),data=chl,family=Gamma(link="log"),
             prior=c(prior(cauchy(0,1),class=sd),
                     prior(normal(0,5),class=b)))
```

Model Checks
```{r}
print(bchlbrm)
pp_check(bchlbrm,type="hist")
pp_check(bchlbrm,type="boxplot")
```

Example of Comparison among Treatments

```{r}
chlpost<-posterior_samples(bchlbrm)
str(chlpost)

bchltrt2_3<-chlpost$b_Intercept+chlpost$b_date0f3+chlpost$b_trt0f2+chlpost$`b_date0f3:trt0f2`
bchltrt4_3<-chlpost$b_Intercept+chlpost$b_date0f3+chlpost$b_trt0f4+chlpost$`b_date0f3:trt0f4`

#Date 3#
#Trt 2 & 4#
bchltrt2_4_d3<-exp(bchltrt2_3)-exp(bchltrt4_3)
mean(bchltrt2_4_d3) #Average of 6.1 higher mg/l from control than selenium
quantile(bchltrt2_4_d3,probs=c(0.025,0.975)) 
sum(bchltrt2_4_d3>0)/4000 #91.5% probability that these treatments are different
```

Preparing to plot

Create data frame, edit date as a properly ordered factor so that it plots dates in the right order, switch date to day of experiment.

```{r}
bchlplot<-marginal_effects(bchlbrm, robust=FALSE)
bchlplot<-as.data.frame(bchlplot$`date0f:trt0f`)
bchlplot$date2<-factor(bchlplot$date0f, levels = c("6/20/2016","6/28/2016", "7/4/2016", "7/12/2016", "7/18/2016", "7/26/2016", "8/2/2016"))

bchlplot$date3<-ifelse(bchlplot$date2=="6/20/2016", "Day 0",
                                         ifelse(bchlplot$date2=="6/28/2016", "Day 7",
                                                ifelse(bchlplot$date2=="7/4/2016", "Day 13",
                                                       ifelse(bchlplot$date2=="7/12/2016", "Day 21",
                                                              ifelse(bchlplot$date2=="7/18/2016", "Day 27",
                                                                     ifelse(bchlplot$date2=="7/26/2016", "Day 35", "Day 42"))))))

bchlplot$date4<-factor(bchlplot$date3, levels=c("Day 0", "Day 7", "Day 13", "Day 21", "Day 27", "Day 35", "Day 42"))
```

Plot

```{r}
ggplot(bchlplot,aes(x=date4,y=estimate__, color=trt0f, group=trt0f))+
  geom_errorbar(aes(ymin=lower__, ymax=upper__), alpha=0.3, width=.1, position=position_dodge(width=0.4))+
  geom_point(position=position_dodge(width=0.4), size=4)+
  geom_line(position=position_dodge(width=0.4))+
  xlab("Day of Experiment")+
  ylab(expression(paste("Benthic Chlorophyll (", mu, "g/cm2)")))+
  scale_color_manual(name="Treatment", labels = c("Control", "Atrazine", "Selenium", "Atrazine and Selenium"),  values = c("grey0", "dodgerblue4","forestgreen","darkorange"))+
  theme_classic()+
  theme(axis.text.x = element_text(color="black"))+
  theme(axis.text.y = element_text(color="black"))+
  theme(legend.title = element_text(face="bold", size="12"))+
  theme(legend.text = element_text(size="12"))
```


Water Column Chlorophyll

Model

```{r}
get_prior(wchl~date0f+trt0f+date0f*trt0f +(1|tank),data=chl,family=Gamma(link="log"))

wchlbrm<-brm(wchl~date0f+trt0f+date0f*trt0f +(1|tank),data=chl,family=Gamma(link="log"),
            prior=c(prior(cauchy(0,1),class=sd),
                    prior(normal(0,5),class=b)))
```

Model Checks

```{r}
print(wchlbrm)
pp_check(wchlbrm,type="hist")
pp_check(wchlbrm,type="boxplot")
```

Example of Comparison among Treatments

```{r}
wchlpost<-posterior_samples(wchlbrm)
str(wchlpost)

wchltrt1_1<-wchlpost$b_Intercept
wchltrt3_1<-wchlpost$b_Intercept+wchlpost$b_trt0f3

#Date 1#
#Trt 1 & 3#
wchltrt1_3_d1<-exp(wchltrt1_1)-exp(wchltrt3_1)
mean(wchltrt1_3_d1) #Average of 2.7 higher mg/l from control than selenium
quantile(wchltrt1_3_d1,probs=c(0.025,0.975)) 
sum(wchltrt1_3_d1>0)/4000 #93% probability that these treatments are different
```

Preparing to plot

Create data frame, edit date as a properly ordered factor so that it plots dates in the right order, change date to day of experiment 

```{r}
wchlplot<-marginal_effects(wchlbrm, robust=FALSE)
wchlplot<-as.data.frame(wchlplot$`date0f:trt0f`)
wchlplot$date2<-factor(wchlplot$date0f, levels = c("6/20/2016","6/28/2016", "7/4/2016", "7/12/2016", "7/18/2016", "7/26/2016", "8/2/2016"))

wchlplot$date3<-ifelse(wchlplot$date2=="6/20/2016", "Day 0",
                         ifelse(wchlplot$date2=="6/28/2016", "Day 7",
                                ifelse(wchlplot$date2=="7/4/2016", "Day 13",
                                       ifelse(wchlplot$date2=="7/12/2016", "Day 21",
                                              ifelse(wchlplot$date2=="7/18/2016", "Day 27",
                                                     ifelse(wchlplot$date2=="7/26/2016", "Day 35", "Day 42"))))))

wchlplot$date4<-factor(wchlplot$date3, levels=c("Day 0", "Day 7", "Day 13", "Day 21", "Day 27", "Day 35", "Day 42"))
```

Plot

```{r}
ggplot(wchlplot,aes(x=date4,y=estimate__, color=trt0f,group=trt0f))+
  geom_errorbar(aes(ymin=lower__, ymax=upper__),alpha=0.3, width=.1, position=position_dodge(width=0.4))+
  geom_point(position=position_dodge(width=0.4), size=4)+
  geom_line(position=position_dodge(width=0.4))+
  xlab("Day of Experiment")+
  ylab("Water Column Chlorophyll (mg/L)")+
  scale_color_manual(name="Treatment", labels = c("Control", "Atrazine", "Selenium", "Atrazine and Selenium"),  values = c("grey0", "dodgerblue4","forestgreen","darkorange"))+
  theme_classic()+
  theme(axis.text.x = element_text(color="black"))+
  theme(axis.text.y = element_text(color="black"))+
  theme(legend.title = element_text(face="bold", size="12"))+
  theme(legend.text = element_text(size="12"))
```

Body Size Models

Data

```{r}
urlfile5<-"https://raw.githubusercontent.com/briannahenry/Mesocosm2/master/chiro_g_ind.csv"
chiro_g_ind<-read.csv(urlfile5)
chiro_g_ind$trt0f<-as.factor(chiro_g_ind$trt)
chiro_g_ind$date0f<-as.factor(chiro_g_ind$date)
chiro_g_ind$morph0f<-as.factor(chiro_g_ind$morph)

urlfile6<-"https://raw.githubusercontent.com/briannahenry/Mesocosm2/master/dragon_g_ind.csv"
dragon_g_ind<-read.csv(urlfile6)
dragon_g_ind$trt0f<-as.factor(dragon_g_ind$trt)
dragon_g_ind$date0f<-as.factor(dragon_g_ind$date)

urlfile7<-"https://raw.githubusercontent.com/briannahenry/Mesocosm2/master/may_g_ind.csv"
may_g_ind<-read.csv(urlfile7)
may_g_ind$trt0f<-as.factor(may_g_ind$trt)
may_g_ind$date0f<-as.factor(may_g_ind$date)
```

Effect of Treatment on Chironomid Body Size

```{r}
get_prior(g_ind~date0f*trt0f*morph0f+(1|tank),data=chiro_g_ind,family=Gamma(link="log"))

chirobody<-brm(g_ind~date0f*trt0f*morph0f+(1|tank),data=chiro_g_ind,family=Gamma(link="log"),
             prior=c(prior(cauchy(0,1),class=sd),
                     prior(normal(0,1),class=b)))
print(chirobody)
pp_check(chirobody,type="hist")
pp_check(chirobody,type="boxplot")

marginal_effects(chirobody, robust=FALSE)
```

Effect of Treatment on Chironomid Body Size

```{r}
get_prior(g_ind~date0f*trt0f+(1|tank),data=dragon_g_ind,family=Gamma(link="log"))

dragonbody<-brm(g_ind~date0f*trt0f+(1|tank),data=dragon_g_ind,family=Gamma(link="log"),
               prior=c(prior(cauchy(0,1),class=sd),
                       prior(normal(0,1),class=b)))

marginal_effects(dragonbody, robust=FALSE)
```

Effect of Treatment on Chironomid Body Size

```{r}
get_prior(g_ind~date0f*trt0f+(1|tank),data=may_g_ind,family=Gamma(link="log"))

maybody<-brm(g_ind~date0f*trt0f+(1|tank),data=may_g_ind,family=Gamma(link="log"),
                prior=c(prior(cauchy(0,1),class=sd),
                        prior(normal(0,1),class=b)))
marginal_effects(maybody, robust=FALSE)
```


Effects of Dragonflies in the Last 3 Weeks

Data

```{r}
urlfile8<-"https://raw.githubusercontent.com/briannahenry/Mesocosm2/master/odononew.csv"
odononew<-read.csv(urlfile8)

odononew$trt0f<-as.factor(odononew$trt)
odononew$date0f<-as.factor(odononew$date)
```

Model with just Date and Treatment as Predictors for last 3 Weeks

```{r}
get_prior(totnonew~date0f*trt0f +(1|tank),data=odononew,family=poisson(link="log"))

abundadultend<-brm(totno~date0f*trt0f +(1|tank),data=odononew,family=poisson(link="log"),
                prior=c(prior(cauchy(0,1),class=sd),
                        prior(normal(0,5),class=b)))


print(abundadultend)
pp_check(abundadultend,type="hist") 
pp_check(abundadultend,type="boxplot")
```

Model with Treatment and Dragonfly Abundance as Predictors, and Date as a Random Effect for last 3 Weeks

```{r}
odomodel2<-brm(totno~trt0f*no_odo +(1|tank/date0f),data=odononew,family=poisson(link="log"),
              prior=c(prior(cauchy(0,1),class=sd),
                      prior(normal(0,5),class=b)))
print(odomodel2)
pp_check(odomodel2,type="hist") 
pp_check(odomodel2,type="boxplot")
```

Model Comparison

```{r}
waic(odomodel2, abundadultend)
```

Odonate Model Plot

```{r}
odomplot<-marginal_effects(odomodel2)
odomplot<-data.frame(odomplot$`no_odo:trt0f`)
odomplot$trt2<-ifelse(odomplot$trt0f=="1", "Control",
                      ifelse(odomplot$trt0f=="2", "Atrazine",
                             ifelse(odomplot$trt0f=="3", "Selenium", "Atrazine and Selenium")))
odomplot$trt3<-factor(odomplot$trt2, levels=c("Control", "Atrazine", "Selenium", "Atrazine and Selenium"))
odomplot$est<-(odomplot$estimate__)*2.78/4
odomplot$lower<-(odomplot$lower__)*2.78/4
odomplot$upper<-(odomplot$upper__)*2.78/4
odomplot$odo<-(odomplot$no_odo)*2.78/4

odomodelplot<-ggplot(odomplot, aes(x=odo, y=est, ymin=lower, ymax=upper, group=trt3))+
      geom_line()+
      geom_ribbon(alpha=0.1)+
      ylab(expression(paste("Non-odonate Adult Insects (#/m"^2,"/day)")))+
      xlab(expression(paste("Odonates (#/m"^2,"/day)")))+
      theme_classic()+
      scale_y_log10()+
      facet_wrap(~trt3, scales="free")

odomodelplot
```


Water Quality Data Plots

Data

```{r}
urlfile9<-"https://raw.githubusercontent.com/briannahenry/Mesocosm2/master/WQ_new.csv"
WQ<-read.csv(urlfile9)

WQ$date2<-factor(WQ$date, levels = c("6/20/2016","6/28/2016", "7/4/2016", "7/12/2016", "7/18/2016", "7/26/2016", "8/2/2016"))
WQ$trt0f<-as.factor(WQ$trt)

WQ$date3<-ifelse(WQ$date2=="6/20/2016", "Day 0",
                     ifelse(WQ$date2=="6/28/2016", "Day 7",
                            ifelse(WQ$date2=="7/4/2016", "Day 13",
                                   ifelse(WQ$date2=="7/12/2016", "Day 21",
                                          ifelse(WQ$date2=="7/18/2016", "Day 27",
                                                 ifelse(WQ$date2=="7/26/2016", "Day 35", "Day 42"))))))
WQ$date4<-factor(WQ$date3, levels=c("Day 0", "Day 7", "Day 13", "Day 21", "Day 27", "Day 35", "Day 42"))
```

Plots

```{r}
######Dissolved Oxygen#####
DOplot<-ggplot(WQ,aes(x=date4,y=do,ymin=sdlow2,ymax=sdhi2,fill=trt0f, shape=trt0f))+
  geom_errorbar(position=position_dodge(width=0.4), alpha=0.3, width=0.1)+
  geom_point(size=4,position=position_dodge(width=0.4))+
  xlab("Day of Experiment")+
  ylab("Dissolved Oxygen (mg/L)")+
  scale_shape_manual(name="Treatment", labels = c("Control", "Atrazine", "Selenium", "Atrazine and Selenium"),  values = c(21,22,23,24))+
  scale_fill_manual(name="Treatment", labels = c("Control", "Atrazine", "Selenium", "Atrazine and Selenium"),  values = c("grey0","grey35","grey70","grey100"))+
  theme_classic()+
  theme(axis.text.x = element_text(color="black"))+
  theme(axis.text.y = element_text(color="black"))+
  theme(legend.title = element_text(face="bold", size="11"))  

DOplot

#####PH####
PHplot<-ggplot(WQ,aes(x=date4,y=ph,ymin=sdlow,ymax=sdhi,fill=trt0f, shape=trt0f))+
  geom_errorbar(position=position_dodge(width=0.4), alpha=0.3, width=0.1)+
  geom_point(size=4,position=position_dodge(width=0.4))+
  xlab("Day of Experiment")+
  ylab("pH")+
  scale_shape_manual(name="Treatment", labels = c("Control", "Atrazine", "Selenium", "Atrazine and Selenium"),  values = c(21,22,23,24))+
  scale_fill_manual(name="Treatment", labels = c("Control", "Atrazine", "Selenium", "Atrazine and Selenium"),  values = c("grey0","grey35","grey70","grey100"))+
  theme_classic()+
  theme(axis.text.x = element_text(color="black"))+
  theme(axis.text.y = element_text(color="black"))+
  theme(legend.title = element_text(face="bold", size="11"))  

PHplot


#####Conductivity#####
condplot<-ggplot(WQ,aes(x=date4,y=cond,ymin=sdlow3,ymax=sdhi3,fill=trt0f, shape=trt0f))+
  geom_errorbar(position=position_dodge(width=0.4), alpha=0.3, width=0.1)+
  geom_point(size=4,position=position_dodge(width=0.4))+
  xlab("Day of Experiment")+
  ylab(expression(paste("Conductivity (", mu, "s/cm)")))+
  scale_shape_manual(name="Treatment", labels = c("Control", "Atrazine", "Selenium", "Atrazine and Selenium"),  values = c(21,22,23,24))+
  scale_fill_manual(name="Treatment", labels = c("Control", "Atrazine", "Selenium", "Atrazine and Selenium"),  values = c("grey0","grey35","grey70","grey100"))+
  theme_classic()+
  theme(axis.text.x = element_text(color="black"))+
  theme(axis.text.y = element_text(color="black"))+
  theme(legend.title = element_text(face="bold", size="11"))  

condplot


####Turbidity#####
turbplot<-ggplot(WQ,aes(x=date4,y=turb,ymin=sdlow4,ymax=sdhi4,fill=trt0f, shape=trt0f))+
  geom_errorbar(position=position_dodge(width=0.4), alpha=0.3, width=0.1)+
  geom_point(size=4,position=position_dodge(width=0.4))+
  xlab("Day of Experiment")+
  ylab("Turbidity (NTU)")+
  scale_shape_manual(name="Treatment", labels = c("Control", "Atrazine", "Selenium", "Atrazine and Selenium"),  values = c(21,22,23,24))+
  scale_fill_manual(name="Treatment", labels = c("Control", "Atrazine", "Selenium", "Atrazine and Selenium"),  values = c("grey0","grey35","grey70","grey100"))+
  theme_classic()+
  theme(axis.text.x = element_text(color="black"))+
  theme(axis.text.y = element_text(color="black"))+
  theme(legend.title = element_text(face="bold", size="11"))  

turbplot


####Temeprature####
tempplot<-ggplot(WQ,aes(x=date4,y=temp,ymin=sdlow5,ymax=sdhi5,fill=trt0f, shape=trt0f))+
  geom_errorbar(position=position_dodge(width=0.4), alpha=0.3, width=0.1)+
  geom_point(size=4,position=position_dodge(width=0.4))+
  xlab("Day of Experiment")+
  ylab(expression("Temperature " ( degree*C)))+
  scale_shape_manual(name="Treatment", labels = c("Control", "Atrazine", "Selenium", "Atrazine and Selenium"),  values = c(21,22,23,24))+
  scale_fill_manual(name="Treatment", labels = c("Control", "Atrazine", "Selenium", "Atrazine and Selenium"),  values = c("grey0","grey35","grey70","grey100"))+
  theme_classic()+
  theme(axis.text.x = element_text(color="black"))+
  theme(axis.text.y = element_text(color="black"))+
  theme(legend.title = element_text(face="bold", size="11"))  

tempplot
```

